The \dealii{} Library, Version 9.0

### 2018-04-23 9.0/paper.tex
Update the particles section.

The major changes of this release are:
\begin{itemize}
\item
  Manifold smoothing: The manifold smoothing algorithms applied in the
  Triangulation class and MappingQGeneric have been changed from the old
  Laplace-style smoothing to a transfinite interpolation that linearly
  blends between the descriptions on the faces around a cell. The old
  transformation introduced boundary layers inside cells that prevented
  convergence rates from exceeding \(3.5\) in the global \(L^2\) errors on typical
  settings. This change also considerably improves mesh quality on settings
  where curved descriptions are only applied to the boundary rather than
  the whole volume.

\item
  A dedicated particles module has been created to provide support for the
  storage of particles and their properties. This module provides a base class
  \texttt{Particles} which represents a particle with position, an ID number and
  a variable number of properties. It also provides a \texttt{ParticleHandler}
  class that manages the storage and handling of particles. This class
  distributes the particles in distributed domains (these are the only domains
  supported by this class so far)

\item
  A dedicated differentiation module has been created to provide support for
  automatic and symbolic differentiation. Automatic differentiation is a set of
  technique to evaluate the derivatives of a function defined by a compute
  program. Currently the Adol-C and Sacado libraries are supported through a
  unified interface. In practice, this support means that Adol-c and Sacado
  data types can be used in the \texttt{FEValues} and \texttt{FEValuesViews}
  to represent degree-of-freedom values.

\item Interfaces to more external libraries and programs.

\item C++11 is now both required and used.

\item
  Support for GPU computations.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Manifolds}

...

@@

...

@@

...

>>>>

The major changes of this release are:
\begin{itemize}
\item xxxx something with manifolds xxx
\item Support for particle-in-cell methods
\item Dedicated support for automatic and symbolic differentiation.
\item Interfaces to more external libraries and programs.
\item C++11 is now both required and used.
\item Support for GPU computations.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{xxx something with Manifolds xxx}

  Manifold smoothing: The manifold smoothing algorithms applied in the
  Triangulation class and MappingQGeneric have been changed from the old
  Laplace-style smoothing to a transfinite interpolation that linearly
  blends between the descriptions on the faces around a cell. The old
  transformation introduced boundary layers inside cells that prevented
  convergence rates from exceeding \(3.5\) in the global \(L^2\) errors on typical
  settings. This change also considerably improves mesh quality on settings
  where curved descriptions are only applied to the boundary rather than
  the whole volume.

@@

While \dealii{} is a package intended to solve problems with the
finite element method -- i.e., using continuous or discontinuous
\textit{fields} --, is often convenient in fluid dynamics problems to
couple the continuum description of phenomena with particles. These
particles, advected along with the numerical approximation of the flow
field, are then either used to visualize properties of the flow, or to
advect material properties such as the viscosity of inhomogenous
mixtures of fluids. If each particle is associated with the cells
of a mesh, these methods are often referred to as particle-in-cell (PIC).

\dealii{} now has a dedicated particles module. The module provides a base class
\texttt{Particle} that represents a particle with position, an ID number and
a variable number of properties. They are jointly represented by a \texttt{ParticleHandler}
class that manages the storage and handling of all particles. In
parallel simulations, this class also
distributes the particles among the subdomains of the parallel process
and supports efficient data transfer during mesh refinement and
checkpoint/restart phases.

A much more detailed view of the underlying algorithms can be found in
\cite{GLHPB18}. A longer report is at \cite{GHPB16}.

@@

A dedicated differentiation module has been created to provide support for
automatic and symbolic differentiation. Automatic differentiation is a set of
technique to evaluate the derivatives of a function defined by a compute
program. Currently the Adol-C and Sacado libraries are supported through a
unified interface. In practice, this support means that Adol-c and Sacado
data types can be used in the \texttt{FEValues} and \texttt{FEValuesViews}
to represent degree-of-freedom values.
